Intended Table of Contents Thesis

### 2013-03-21 Chapters/Chapter1/paper_list.tex
Work of wednesday 20 march

  \item ``Time series segmentation for context recognition in mobile devices'', \cite{himberg2001time}, cited: 151, 2001. Splits and merges segments, while keeping k constant using cost function on segments for internal heterogeneity. Multiple instances determine number of k. Microphone and accelerometer data, in front of chest. ARtificial data

@@

\subsubsection{Pure segmentation}
\begin{itemize}
  \item ``Bayesian Online Changepoint Detection'', \cite{adams2007bayesian}, cited: 67, 2007. Uses a priori and posteriori distribution prediction of the current run-length. Online. Uses well-drilling data, Dow Jones return value and coal-mine accidents rate, which are all used by others. Does not compare results. Decouples algorithm from model (?).
  \item CUSUM Method: piece wise segments of gaussian mean with noise. More refs needed.
  \item ``An Automatic Segmentation Technique in Body Sensor Networks based on Signal Energy'', \cite{guenterberg2009automatic}, cited: 13. Automatic segmenting, adaptive threshold. Pure segmenting, no classification. Nice and clean method? Weakness: single action segmented as multiple. Used multiple sensors.
  \item ``Segmenting Motion Capture Data into Distinct Behaviors'', \cite{barbivc2004segmenting}, cited: 242, 2004. On-line methods: cut-points on increased intrinsic dimensionality, distribution of poses is observed to change. Batch: cut when consecutive frames belong to different Gaussian mixture models. Fixed fourteen motions, compared with manual segmentation. Uses PCA and Probabilistic PCA (models the non-pc subspaces as noise). PPCA is the best. (paper anne)
\end{itemize}

>>>>

  \item ``Time series segmentation for context recognition in mobile devices'', \cite{himberg2001time}, cited: 151, 2001. Splits and merges segments, while keeping k constant using cost function on segments for internal heterogeneity. Multiple instances determine number of k. Microphone and accelerometer data, in front of chest. Artificial data

@@

\subsubsection{Pure segmentation}
  \item ``Bayesian Online Changepoint Detection'', \cite{adams2007bayesian}, cited: 67, 2007. Uses a priori and posteriori distribution prediction of the current run-length. Online. Uses well-drilling data, Dow Jones return value and coal-mine accidents rate, which are all used by others. Does not compare results. Decouples algorithm from model (?).
  \item CUSUM Method: piece wise segments of gaussian mean with noise. More refs needed.
  \item ``An Automatic Segmentation Technique in Body Sensor Networks based on Signal Energy'', \cite{guenterberg2009automatic}, cited: 13. Automatic segmenting, adaptive threshold, standard deviation, niet bayesian. Pure segmenting, no classification. Nice and clean method? Weakness: single action segmented as multiple. Used multiple sensors.
  \item ``Segmenting Motion Capture Data into Distinct Behaviors'', \cite{barbivc2004segmenting}, cited: 242, 2004. On-line methods: cut-points on increased intrinsic dimensionality, distribution of poses is observed to change. Batch: cut when consecutive frames belong to different Gaussian mixture models. Fixed fourteen motions, compared with manual segmentation. Uses PCA and Probabilistic PCA (models the non-pc subspaces as noise). PPCA is the best. (paper anne). From computer graphics / motion capture data.
  \item ``Activity recognition using inertial sensing for healthcare, wellbeing and sports applications: A survey'', \cite{avci2010activity}, cited: 22, 2010. Discusses segmentation as form of sliding window, top-down, bottom-up or swab. Interesting overview of five steps: preprocessing, segmentation, feature extraction, dimensionality reduction and classifiers. Classifiers only with fixed number of activities (no non-parametric).
  \item ``Event Detection From Time Series Data'', \cite{guralnik1999event}, cited: 291, 1999. Iterative (online, incremental) method to fit model to segment, likelihood to determine if partitioned further (number of change points), when batch. Maximum likelihood methods. Also model selection, loss and risk functions. With incremental (online) method, every new data point had likelihood criteria of being a new segment or current one. If no segment for long time, computations become increasingly expensive. Solution: sliding window for last $w$ points only.
  \item ``An adaptive approach for online segmentation of multi-dimensional mobile data'', \cite{guo2012adaptive}, cited: 1, 2012. Adaptive model for selecting suitable dimensions to build model and select model (linear, quadratic, cubic). Multiple metric for results evaluation; traditional regression error, information retrieval (precision, recall, F-measure) and segmentation delay. Uses three-axis accelerometer data. Extends the SWAB method. Natural setting, no restriction on body location.
  \item ``Activity Recognition on 3D Accelerometer Data (Technical Report)'', \cite{bernecker2012activity}, cited: 0, 2012. First makes distinction between periodic and non-periodic activities, directly on accelerometer data. Autocorrelation as a measure for self-similarity (periodicy). After segmentation, features are extracted for clustering. Then dimensionality reduction and (re)classification. Interesting post-processing; small segments with neighbors of the same activity are merged. Removes small mis-activities.
  \item ``Change-Point Detection in Time-Series Data by Direct Density-Ratio Estimation'', \cite{kawahara2009change}, cited: 41. Non-parametric approach, online method, no strong model assumptions. Uses multiple datasets, origin referenced. Much follow-up work done. Artificial datasets. (no sensors) Uses likelihood/density ratios estimator, not the densities themselves. Probability distributions that generate the time series.
  \item ``Adaptive Filtering and Change Detection'' (book), \cite{gustafsson2000adaptive}, cited: 682 (!!), 2000. Lots of algorithms, hard to read.
  \item ``Online segmentation of time series based on polynomial least-squares approximations'', \cite{fuchs2010online}, cited: 17, 2010. Creates higher-order polynomial model of data, sliding and growing window. Works well for traditional time series (stocks), but not for non-stationary such as daily life.
  \item ``Novel online methods for time series segmentation'', \cite{liu2008novel}, cited: 17, 2008. (Stepwise) Feasable Space Window. Compares with SWAB. Referenced in \cite{guo2012adaptive}, but that one choses SWAB because it should be lower time complexity and fast. (S)FSW creates less segments, while SWAB has lower error. FSW is fastest and reliable (due to this paper self).
  \item ``An adaptive cusum-based test for signal change detection'', \cite{alippi2006adaptive} cited: 16, 2006. CUSUM-test with adaptive parameter settings. Can detect non-stationary processes by drift of signal. Applicable for extracted features, e.g. mean.
